Agenda diversity and coverage bias: A quantitative approach to the agenda-setting theory

### 2018-08-28 bmc_article.tex
Version corregida por balen a ver lectura mas o menos definitiva

%%% Load packages
\usepackage{amsthm,amsmath}
%\RequirePackage{natbib}
%\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
%\RequirePackage{hyperref}
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails

@@

\par This can be observed in figure \ref{fig:all_agenda} where the time evolution of the topics is shown in a bump chart of the Agendas. The bump chart provides  a clear visualization of the relative weight of the topics at the same time that their ranking. In  this figure  we also highlight some important events related to the dynamics of the topics and  it is  possible to appreciate how the main topic change in time and have a glance of the qualitative differences between agendas. In particular, it can be observed some differences between Public Agendas ($GT$ and $Tw$) that were not observed in the previous figure:

IN PARTICULAR.. COMENTAR MAS DE ESTE GRAFICO

\par The linear correlations shown in table \ref{table:gt_all_correlation} are  positive and statistically significant in all the cases, This can be interpreted as a validation of the topics found in the corpus and the keywords that describe it. Even though it is expected that the Media's and public's interest should generally follow a similar a pattern due to the external events, we are interested in those periods where they significantly differ. 
A non positive (or a non significant) correlation may imply, besides the obvious conclusion of agenda's disengagement, that we could eventually fail in properly detect the keywords or features that describe a particular topic, so the Google Trends' or Twitter's pattern would not be able to reflect a similar behavior that its counterpart in the Media.

@@

\par In order to quantify the diversity of the Agendas, we start by representing them as distributions in the topic's space. 
Following \cite{boydstun2014importance}, we calculate the normalized Shannon's entropy ($H$, see eq.\ref{eq:shannon_entropy}) in order to measure the diversity of the \textbf{MA} and \textbf{PA}.
\par In figure \ref{fig:shannon_entropy_agendas} we can see the value of $H$ as a function of time, where it can be focused in those periods of time where the diversity is lower than usual. This effect is notoriously more pronounced in the Public Agenda giving by \textbf{GT}, and in particular in four specific days  where can be detected four local minima of Shannon's entropies. Three of them are outliers as defined in section \ref{sec:MatMeth}, two of them from \textbf{GT} and one from \textbf{Tw}. 
\par A lower value in the agenda's diversity is due to the fact that the most important topic attracts practically all the attention of the public and the media.
In the radar plots included in figure \ref{fig:shannon_entropy_agendas} we can see that two of these outliers (\textbf{a} and \textbf{d}) belong to the topic \emph{Elections} and are related with the primary and general legislative elections that took place in August 13th and October 22th. 
In all the agendas these points where detected as outliers except point (d) in Twitter Agenda. Why is that? The radar plot of the Twitter agenda for this day displays an association between the topic \emph{Elections} and the \emph{Current President} which could be decreasing the important of this topic.
Discussions in Twitter about elections appear also in point (c), when the other agendas seems to be more diverse. 
On the other hand, we focused in point (b), despite not being detected as a outlier, because it belong to the topic \emph{Missing person} and this date correspond to the rally that took place one month after the disappearance of \emph{Santiago Maldonado} (see section \ref{sec:Context}). It is important to notice that the Shannon's Entropy of GT Agenda displays a minimum (collapsing agenda) not shown neither in the Media nor in the Twitter Agendas.
We emphasize the discussion about this topic because we can appreciate  interesting facts that appear along the analysis.
\par From the measure of $H$ we can also see that the median of the Public Agenda diversity is statistical significant lower than the Media Agenda's one.
Specifically $H_{GT} = 0.73$ and $H_{Tw} = 0.74$ are statistical significant lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
However from figure \ref{fig:shannon_entropy_agendas} we can see that \textbf{GT} shows more abrupt dropouts in the diversity in response to specific events.
We conclude that its an important fact about audience behavior: given a finite set of topics, \textbf{the Public Agenda is less diverse than the Media Agenda}, because the public seems to focus more in the most important topic than the Media can do, maybe due to editorial decisions.

@@

\par Given our interpretation of the Agendas as time-evolving distributions, we can  compare them by computing the Jensen-Shannon distance. In this context, outliers in selected dates will correspond to divergences between Public and Media Agenda, i.e., specific events where the public interest do not match with media offer.
In figure \ref{fig:jensen_shannon_gt} we show the Jensen-Shannon distance between Media and Publics Agendas as a function of time. We focus in three points that seems to be relevant enough. In all cases, the topic distributions at that particular dates displayed by  the radar plots shows that a greater distance is associated with a more interest of public in the topic \emph{Missing person}. 
\par Points \textbf{(c)} and \textbf{(d)} shows that both the Public and the Media highlight this topic, but the Media do not disregard other topics, so the corresponding distance between them can be interpreted  of another way of seeing the diversity effect discussed in the last section.
\par On the other hand,  points \textbf{(a)} (we take this point due to be a local maximum despite not being an outlier) and \textbf{(b)} seem to show an interest of the public in the topic \emph{Missing person} which it is not reflected in the Media.  In figure \ref{fig:all_agenda} we can see that this topic becomes the most important in public's interest (both \textbf{GT} and \textbf{Tw}) days before that  it happen in the Media Agenda. It can be associates  with a social networks (like Facebook and Twitter) campaign  in favor  of the appearance of \emph{Santiago Maldonado} (``The missing person") that took place on  August 26th. It was very important and was initially underestimated by the main Media outlets in Argentina (see section \ref{sec:Context}). 
\par It is important to notice that it is our interpretation of the data based on the knowledge of the context, and  we are not measuring causality between Agendas (we will say a few words about it in section \ref{sec:who_sets}), i.e. we can't say, for instance, that in this case the Public Agenda set the Media Agenda. 
However, the Jensen-Shannon distance, in conjunction with the measurement of the agenda diversity given by the Shannon entropy, give an insight of independent behavior of the Public and the Media, and its identification can be a starting point to study the Media reaction to a change in audience's interests.

@@

\par In this section we leave aside the Public Agenda as a whole and we study how the Media agenda of each media outlet. 
In figure \ref{fig:news_agenda} we show the bump charts corresponding to each newspaper analogously to figure \ref{fig:all_agenda}.
The topics are the same introduced in the wordclouds of figure \ref{fig:topics_wordclouds}, but when computing the topics' weights,  the articles are discriminated by newspaper. 
We also show the radar plots showing the average distribution, as made in figure \ref{fig:topics_wordclouds}. 
\par In figure \ref{fig:news_agenda} we can see in a qualitative way the slightly differences between the newspapers' agendas.
For instance, we can see how newspaper called \emph{P\'agina 12} gave more importance to the topics \emph{Missing person} and \emph{Social leader}, while it reduces to minimum the coverage of the topic  \emph{Former Planning minister} as the others did.

\par In other to detect outliers behavior of a given newspaper respect to the others, we again calculate the Jensen-Shannon distance between the newspapers agenda and the Media Agenda.
Note that this is the distance between the distributions of figure \ref{fig:news_agenda} and the top panel of figure \ref{fig:all_agenda}.
\par In figure \ref{fig:jensen_shannon_news} we show the Jensen-Shannon distance as a function of time.
We detect three points as outliers, although we discard the point \textbf{(b)} due to the low information of \emph{Infobae} in that period. 
The other two points corresponds to differences between \emph{P\'agina 12} and the other newspapers and correspond to differences in the coverage of the topic \emph{Missing person}.

\par The point \textbf{(a)} corresponds  to the first news of the Santiago Maldonado's disappearance  reported by \emph{P\'agina 12} before the primary elections, and in point \textbf{(c)} to  the two months rally after the disappearance took place (see section \ref{sec:Context}). Another difference in point \textbf{(c)} corresponds to a greater coverage of \emph{P\'agina 12} in the topic \emph{Social leader} where the others media outlets seem to be more interested in the topic \emph{Former Vice-President}.

@@

\par From panel (a) of figure \ref{fig:topics_temporal_profiles}, we can see the larger coverage of \emph{P\'agina 12} respect the other newspapers at the beginning of the period. We can, for instance, quantify this difference calculating  the median of the signals. If we focus in the period between July 31th and August 27th, the median of the topic's relative weight for \emph{P\'agina 12} is roughly 0.14 and this is statistically significant larger ($p < 10^{-7}$) than other medians, which are lower than 0.05.
Analyzing the same period, but in panel (b), we again can show that the median in \emph{P\'agina 12}, which is roughly 0.01, is lower than the others, which oscillate around 0.05 ($p<10^{-3}$)
This quantification is proposed as method of studying coverage bias in the context of the methodology implemented in our work.

\par Finally, in figure \ref{fig:topics_temporal_profiles} we also show word-clouds of topic's keywords but separating those who are more frequently mentioned by each newspaper, and filtering the words that are common to all and basically define the factual details of the topic.
Although most of the words are not relevant enough, some of them are quite interesting, as for instance the word \emph{represi\'on} (repression) when \emph{P\'agina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (Fern\'andez de Kirchner, former president) which is employed by all newspapers except \emph{P\'agina 12} when they  talk about the topic \emph{Former Planning minister} (see section \ref{sec:Context}).
We think that a more deeply study of topics' keywords could be a first approximation in the study of framing, which will constitute the core of futures works.

\subsection*{After all: Who sets the Agenda?}
\label{sec:who_sets}

\par The behavior of the Media Agenda and the Public one, either by looking at Google Trends or Twitter, shows periods when there is a strong similarity among them (mostly in the presence of an unexpected event) and periods when they seem to be unrelated. These are mere observation that talk about the correlation between the agendas.
However the agenda-setting theory is in its nature a theory about causality: Is the audience a passive actor who follows what the Media says, or there are periods where the Media must paid attention at public's interests?
Paraphrasing the question, who sets the agenda, the Media or the audience?
In a world where social media exists and the feedback between a Media and its audience is common currency, nowadays the idea that the Media sets the agenda and the audience blindly follows it (as it's seemed to be suggested in the original work of McCombs) is too naive.

\par In spite of the fact that we think that to establish a causation, i.e. the direction towards information flows, is a task that must be made with extreme care, we have something to say in this work about causality. 
We think that the \emph{Missing person} topic is the most adequate topic to be discussed because:
\begin{itemize} 
\item It caused a great impact in either the Media and the audience
\item  its coverage fully deploys along the time lapse analyzed in this manuscript (see section \ref{sec:Context}).
\end{itemize}

@@

\par Is this a case of reverse agenda-setting, i.e, when the audience set the Media Agenda? 
After all,  the audience get involved about this topic by the Media, so how was the coverage before those events?
By calculating the cumulative sum we can see  the cumulative coverage during the first events related to the topic. 
This measure can be seen as the numerical integrate of the temporal profiles of figure \ref{fig:topics_temporal_profiles} between the initial date and the current date. 
It is interesting to note that the newspaper responsible to accumulate coverage during the initial stage was the minority one: \emph{P\'agina 12}. 
Our interpretation about the setting agenda dynamics of this particular topic is the following: A small newspaper (\emph{P\'agina 12}) gives great coverage to this topic; it is amplified  by public in the social networks and also expressed  by reiterative Google searches. Then the rest of the Media  pay attention to this subject and it becomes an important topic in the Media Agenda. 
This interpretation try to catch in a qualitative way how the information flow was in this specific topic.
On the other hand, behind this interpretation there are two important facts that must be mentioned: First, the disappearance of a person is a very sensible theme for the Argentinian society, and second, there are political reasons in why \emph{P\'agina 12} was particularly interested in cover this topic while the other Media did not follow this interest (see section \ref{sec:Context}).

\par We took the question about causality only in a qualitative way. 
There are different metrics that would help in this question, such as Granger causality or correlation by sliding windows. We think that this analysis must be performed with extreme care since the acquirement of the data.
With this work we aimed to provide a quantitative characterization of the behavior of the Media and the Public but not to establish direction of causation, which we hope this to be the core of future ones.

@@

\par The study of Mass Media, and in particular the agenda setting theory, can be empowered by the used of data mining or machine learning algorithms. 
In this work, through the implementation of a topic detection algorithm we could describe the Agenda of the Media as a distribution which evolves over time and which is defined in a topic's space which emerges from the analysis of the corpus.
This gave us an insight of how we can construct and follow the Public's interests, the Public Agenda, in order to compare with the Media Agenda, i.e. Media interests. 
\par Given the Agendas, we found that the Public one is usually less diverse than the Media, showing that when there is a very attractive topic, the audience focus on this one, when the Media has to cover the other too. 
On the other hand, the measurement of distances between Agendas can be employed to rapidly detect periods when the Public may have an independent behavior respect to the Media. The methodology implemented here also allow us to detect coverage bias in newspapers and gave us a first approximation in the theory of framing. 
\par We hope that some of the elements studied here will give us insights at the time of proposing a mathematical model about Mass Media and Public interaction. Future works may include a more systematic study and its extension to international Media, a deeper study of framing through topic detection and sentiment analysis, and a more quantitative analysis about causality.

@@

\subsubsection*{Current President}
\par \emph{Mauricio Macri} is the current Argentinian President, since December 2015. 
Most articles in political sections are logically devoted to him under different contexts.
However, it is important to point out that during the period analyzed, and specially after the general elections of October 22th, a controversial labour reform promoted by the government was been discussing.

\subsubsection*{\emph{Missing Person}}
\par \emph{Santiago Maldonado} vanished on August 1st after a minor clash between the Gendarmerie (Border Guards) and a group of Mapuches, which recognize as themselves the original population of an area in the Patagonia.
Since that event, the \emph{Mauricio Macri}'s administration was accused by several people as the responsible of a \textbf{forced disappearance}. 
\par A very massive campaign in social media took place on August 26th, under the motto ``Where is Santiago Maldonado?", followed by two massive protest marches to the \emph{Plaza de Mayo} that took place on September 1st and October 1st, which the first one had a great repercussion due to several incidents that took place during the march.
\par The body of \emph{Santiago Maldonado} was found on 17th October in the \emph{Chubut} river, near the place where he was seen the last time, and the autopsy report told that \emph{Santiago Maldonado} had died from ``asphyxia after being submerged", with no injuries on his body. 
However the responsibility of the current administration is still being discussed.

@@

\par \emph{Julio de Vido} was the Planning minister during the administration of \emph{N\'estor Kirchner} and \emph{Cristina Fern\'andez de Kirchner} (2003-2015). In 2015, he was elected to integrate the Chamber of Deputies, which finally voted to strip \emph{De Vido} of his congressional immunity over corruption allegations and was immediatly jailed on October 27th.

\par \emph{Amado Boudou} was the Vice-President of the \emph{Cristina Kirchner}'s administration.
\emph{Boudou} was arrested on November 3th on charges including money-laundering and hiding undeclared assests.

@@

\par Naturally the topics found with LDA may not coincide with the NMF ones.
However, one expects that the corpus under studying should be in some manner robust to the election of the topic model.
On the other hand, as was discussed in \cite{o2015analysis}, NMF can be a more suitable topic modeling method in certain domains, in the way that it produces more coherent topics, while LDA tends to return higher levels of generality and redundancy. Topic coherence is defined as the semantic interpretability of the terms used to describe a particular topic, although the coherence of a topic may depend on the end user's expectations.

@@

\begin{figure}[h!]
\includegraphics[width = \textwidth]{Fig1.pdf}
\caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic distribution and their corresponding wordclouds.} The Public Agenda is represented either by Google Trends (GT) and Twitter (Tw). 
Topics names are introduced together with the wordclouds containing the most important keywords involved in the definition of each topic. In green color we show the keywords used to define the topics in the Google Trends and Twitter queries (see table \ref{table:gt_queries}) and therefore in our construction of the Public Agenda.}
\label{fig:topics_wordclouds}
\end{figure}

\begin{figure}[h!]
\includegraphics[width = \textwidth]{Fig2.pdf}
\caption{\textbf{Bump graph of the Media Agenda (MA) and Public Agenda extracted from Google Trends (GT) and Twitter (Tw)}. The curves width and their ordering are related to the topics relative weight. Some important events related to the topics are pointed out:
\textbf{A}: First news about Santiago Maldonado's disappearance;
\textbf{B}: Primary elections;
\textbf{C}: March one month after Santiago Maldonado's disappearance;
\textbf{D}: March two months after Santiago Maldonado's disappearance;
\textbf{E}: Appearance of Santiago Maldonado's body;
\textbf{F}: General elections;
\textbf{G}: Julio De Vido's detention;
\textbf{H}: Debates on labor reform;
\textbf{I}: Amado Boudou's detention.
A more detailed explanation is given in section \ref{sec:Context}.}
\label{fig:all_agenda}
\end{figure}

\begin{figure}[h!]
\includegraphics[height=0.7\textheight]{Fig3.pdf}
\caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda show a less diverse behavior than the Media Agenda as can be seen in the left figure. The horizontal lines are the lower inner fences of each signal in order to identify outliers. The related radar plots shows that those dates when the agenda has a low diversity, the most important topic catches the most public’s attention. \textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
\label{fig:shannon_entropy_agendas}
\end{figure}

>>>>

%%% Load packages
%\usepackage{amsthm,amsmath}
%\RequirePackage{natbib}
%\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
%\RequirePackage{hyperref}
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails

@@

\par This can be observed in figure \ref{fig:all_agenda} where the time evolution of the topics is shown in a bump chart of the Agendas. The bump chart provides  a clear visualization of the relative weight of the topics at the same time that their ranking. In  this figure  we also highlight some important events related to the dynamics of the topics and  it is  possible to appreciate how the main topic change in time and have a glance of the qualitative differences between agendas. In particular, it can be observed some differences between Public Agendas ($GT$ and $Tw$) that were not observed in the previous figure, as for instance, the persistency of main topics is longer in Twitter than in Google Trends. This is more evident at the end of the analyzed period, where topics discussed in Google Trends shows more  responsive to change in Media Agenda than in Twitter, suggesting the existence that the interaction between people is stronger in the analyzed social network.

\par We also calculate linear correlations between same topics of $PA$ and $MA$  and we found that they are  positive and statistically significant in all the cases, as shown in table \ref{table:gt_all_correlation}.  This can be interpreted as a validation of the topics found in the corpus and the keywords that describe it. Even though it is expected that the Media's and public's interest should generally follow a similar a pattern, mainly driven by  external events, we are interested in those periods where they significantly differ. 
A non positive (or a non significant) correlation may imply, besides the obvious conclusion of agenda's disengagement, that we could eventually fail in properly detect the keywords or features that describe a particular topic, so the Google Trends' or Twitter's pattern would not be able to reflect a similar behavior that its counterpart in the Media.

@@

\par How dominant is a main topic? Is the degree of dominance of a given topic in the Media Agenda reflected in the Public Agenda? In order to answer such kind of questions it is necessary  to quantify the diversity of the Agendas, which are represented as  distributions in the topic's space as was shown above.
Following \cite{boydstun2014importance}, we calculate the normalized Shannon's entropy ($H$, see eq.\ref{eq:shannon_entropy}) in order to measure the diversity of the \textbf{MA} and \textbf{PA}.
\par In figure \ref{fig:shannon_entropy_agendas} we can see the value of $H$ as a function of time for the three agendas. It is important to pay attention to those periods of time where the diversity is lower than usual. This effect is notoriously more pronounced in the Public Agenda giving by \textbf{GT} and, in particular, in four specific days  where  four local minima of Shannon's entropies can be detected. Three of them are outliers as defined in section \ref{sec:MatMeth}, two of them from \textbf{GT} and one from \textbf{Tw}. The other one is not an outlier but a pronounced minima and therefore a point of interest in this description.

\par A lower value in the agenda's diversity is due to the fact that the most important topic attracts practically all the attention of the public and the media, collapsing the diversity of the agenda.
In the radar plots included in figure \ref{fig:shannon_entropy_agendas} we can see how two of these outliers (\textbf{a} and \textbf{d}) belong to the topic \emph{Elections}. They are related to the primary and general legislative elections that took place in August 13th and October 22th respectively.
In all the agendas these points were detected as outliers except point (d) in Twitter Agenda. Why is that? The radar plot of the Twitter agenda for this day displays an association between the topic \emph{Elections} and the \emph{Current President}, decreasing the important of this topic.
Discussions in Twitter about elections appear also in point (c), when the other agendas seems to be more diverse. 
On the other hand, and despite not being classified as outlier, we also focus in point (b) because Shannon's Entropy of $GT$ Agenda displays a minimum (collapsing agenda) which is not corresponded neither in the Media nor in the Twitter Agendas. Crawling in the context, we see that it belong to the topic \emph{Missing person} and this date correspond to the rally that took place one month after the disappearance of \emph{Santiago Maldonado} (see section \ref{sec:Context}). 
We  would like to emphasize the discussion about this topic (\emph{Missing person}) because its dynamics show interesting features, as we will show bellow.

\par From the measure of $H$ we have also observed that the median of the Public Agenda diversity is statistical significant lower than the Media Agenda's one.
Specifically $H_{GT} = 0.73$ and $H_{Tw} = 0.74$ are statistical significant lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
However from figure \ref{fig:shannon_entropy_agendas} we can see that \textbf{GT} shows more abrupt dropouts in the diversity in response to specific events.
From all this analysis we  can conclude that given a finite set of topics, \textbf{the Public Agenda is less diverse than the Media Agenda}, because the public seems to focus in the most important topics than Media can do, maybe due to editorial decisions.

@@

\par Given our descriptions of the Agendas as time-evolving distributions, we can  compare them by computing the Jensen-Shannon distance. In this context, outliers in selected dates will correspond to divergences between Public and Media Agenda, i.e., specific events where the public interest do not match with media offer.
In figure \ref{fig:jensen_shannon_gt} we show the Jensen-Shannon distance between Media and Publics Agendas as a function of time. We focus in three points that seems to be relevant enough. In all cases, the topic distributions at that particular dates displayed by  the radar plots show that the increment in the distance between agendas is due to a greater interest of public opinion in the topic \emph{Missing person}.

\par Points \textbf{(c)} and \textbf{(d)} show that both the Public and the Media highlight this topic, but the Media do not disregard other topics, so the corresponding distance between them can be interpreted as lack of the diversity in Public Agenda as discussed in the last section.

\par On the other hand,  points \textbf{(a)} (we take this point due to be a local maximum despite not being an outlier) and \textbf{(b)}  show a major  interest of the public in the topic \emph{Missing person} which it is not reflected in the Media.  In figure \ref{fig:all_agenda} we can see that this topic becomes the most important in public's interest (both \textbf{GT} and \textbf{Tw}) days before that  it happen in the Media Agenda. It can be associates  with a social networks (like Facebook and Twitter) campaign  in favor  of the appearance of \emph{Santiago Maldonado} (``The missing person") that took place on  August 26th. This campaign was massive and  initially underestimated by the main Media outlets in Argentina (see section \ref{sec:Context}).

\par % It is important to notice that it is our interpretation of the data based on the knowledge of the context, and  we are not measuring causality between Agendas (we will say a few words about it in section \ref{sec:who_sets}), i.e. we can't say, for instance, that in this case the Public Agenda set the Media Agenda. 
Finally, it is important to say that the Jensen-Shannon distance, in conjunction with the measurement of agenda diversity given by the Shannon entropy, give an insight of independent behavior, in certain particular dates,  of the Public and the Media. Its identification can be a starting point to study the Media reaction to a change in audience's interests.

@@

\par In this section we leave aside the Public Agenda as an unified corpus and we study the composition and evolution of the Media Agenda of each media outlet. 
In figure \ref{fig:news_agenda} we show the bump charts corresponding to each of the analyzed newspaper analogously to figure \ref{fig:all_agenda}.
The topics are the same introduced in the wordclouds of figure \ref{fig:topics_wordclouds}, but when computing the topics' weights,  the articles are discriminated by newspaper. 
We also show the radar plots showing the average distribution, as made in figure \ref{fig:topics_wordclouds}.

\par In figure \ref{fig:news_agenda} we can qualitative have a glance of the  differences between the newspapers' agendas.
For instance, we can see how the newspaper called \emph{P\'agina 12} gave more importance to the topics \emph{Missing person} and \emph{Social leader}, while it reduces to minimum the coverage of the topic  \emph{Former Planning minister} as the others did.

\par In other to detect significative bias coverage of a given newspaper, we again calculate the Jensen-Shannon distance, but between the individual newspapers agenda and the Media Agenda.
Note that this is the distance between the distributions of figure \ref{fig:news_agenda} and the top panel of figure \ref{fig:all_agenda}. 
 In figure \ref{fig:jensen_shannon_news} we show the Jensen-Shannon distance as a function of time.
We detect three points as outliers, although we finally disregarded point \textbf{(b)} due to a lack of  information of newspaper \emph{Infobae} in that period. 
The other two points corresponds to differences between \emph{P\'agina 12} and the other newspapers and correspond to differences in the coverage of the topic \emph{Missing person}.

\par The point \textbf{(a)} corresponds  to the first news of the Santiago Maldonado's disappearance  reported by \emph{P\'agina 12} before the primary elections and the point \textbf{(c)} corresponds to  the two months' rally after the disappearance  (see section \ref{sec:Context}). Another singularity of point \textbf{(c)} corresponds to a greater coverage of \emph{P\'agina 12} in the topic \emph{Social leader} where the others media outlets seem to be more interested in the topic \emph{Former Vice-President}.

@@

\par From panel (a) of figure \ref{fig:topics_temporal_profiles}, we can see the larger coverage of \emph{P\'agina 12} in comparison to other newspapers at the beginning of the period. We can, for instance, quantify this difference calculating  the median of the signals. If we focus in the period between July 31th and August 27th, the median of the topic's relative weight for \emph{P\'agina 12} is roughly 0.14 and this is statistically significant larger ($p < 10^{-7}$) than other medians, which are lower than 0.05.
Analyzing the same period, but in panel (b), we again can show that the median in \emph{P\'agina 12}, which is roughly 0.01, is lower than the others, which oscillate around 0.05 ($p<10^{-3}$)
This quantification is proposed as method of studying coverage bias in the context of the methodology implemented in our work.

\par Finally, in the same figure \ref{fig:topics_temporal_profiles} we also show wordclouds of topic's keywords highlighting the more frequently mentioned in each newspaper and filtering the common words to all newspapers.
Although most of the words are not relevant enough, some of them are quite interesting, as for instance the word \emph{represi\'on} (repression) when \emph{P\'agina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (Fern\'andez de Kirchner, former president) which is employed by all newspapers except \emph{P\'agina 12} when they  talk about the topic \emph{Former Planning minister} (see section \ref{sec:Context}).
We think that a more deeply study of topics' keywords could be a first approximation in the study of framing, which will constitute the core of futures works.

\subsection*{A brief discussion about  Agenda-Setting}
\label{sec:who_sets}

\par In a world where social media exists and the feedback between a Media and its audience is common currency, nowadays the idea that the Media sets the agenda and the audience blindly follows it (as it's seemed to be suggested in the original work of McCombs) is too naive. Based in the data analyzed above, the behavior of the Media  and Public Agendas, either by looking at Google Trends or Twitter, shows periods of strong similarity  (specially in the presence of unexpected event) and periods of disengagement and therefore is not trivial to establish a causal relationship between agendas, specially when they are represented as evolving in time topic distribution as we did in this work. However, it is possible to discuss agenda setting if we focus in a single topic. We think that the \emph{Missing person} topic is the most adequate topic to be discussed because:
\begin{itemize} 
\item It caused a great impact in either the Media and the audience
\item  its coverage fully deploys along the time lapse analyzed in this manuscript (see section \ref{sec:Context}).
\end{itemize}

@@

\par Is this a case of reverse agenda-setting, i.e, when the audience set the Media Agenda? 
After all,  the audience get involved about this topic by the Media, so how was the coverage before those events?
We can answer these questions by calculating the cumulative coverage of this topic since the first events took place.
This measure can be seen as the numerical integrate of the temporal profiles of figure \ref{fig:topics_temporal_profiles} between the initial date and the current date. 
It is interesting to note that the newspaper responsible to accumulate coverage during the initial stage was the minority one: \emph{P\'agina 12}. 
Our interpretation about the setting agenda dynamics of this particular topic is the following: A small newspaper (\emph{P\'agina 12}) gives great coverage to this topic; it is amplified  by public in the social networks and also expressed  by reiterative Google searches. Then the rest of the Media  pay attention to this subject and it becomes an important topic in the Media Agenda. 
This interpretation try to catch in a qualitative way how the information flow was in this specific topic.
On the other hand, behind this interpretation there are two important facts that must be mentioned: First, the disappearance of a person is a very sensible theme for the Argentinian society, and second, there are political reasons in why \emph{P\'agina 12} was particularly interested in cover this topic while the other Media did not follow this interest (see section \ref{sec:Context}).

\par Even tough we face the question about causality only in a qualitative way and just for a specific topic, it was possible to highlight  the complex feedback dynamics that take place between public and media agendas.
%There are different metrics that would help in this question, such as Granger causality or correlation by sliding windows. We think that this analysis must be performed with extreme care since the acquirement of the data. With this work we aimed to provide a quantitative characterization of the behavior of the Media and the Public but not to establish direction of causation, which we hope this to be the core of future ones.

@@

\par The  Mass media play a fundamental rol in opinion formation and therefore it's of vital importance to have an accurate  quantitative description of the Media  and Public Agenda and their relationship in the framework of Agenda Setting theory.
In this work, through the implementation of a topic detection algorithm we describe the Agenda of the Media as a distribution which evolves in time and which is defined in a topic's space which emerges from the analysis of the corpus. This gave us an insight of how we can construct and follow the Public's interests, the Public Agenda, in order to compare with the Media Agenda, i.e. Media interests.

\par Given the Agendas, we found that the Public one is usually less diverse than the Media, showing that when there is a very attractive topic, the audience focus on this one, meanwhile the Media keeps certain degree of diversity. 
On the other hand, the measurement of distances between Agendas can be employed to rapidly detect periods when the Public may have an independent behavior respect to the Media. The methodology implemented here also allow us to detect coverage bias in newspapers and gave us a first approximation in the theory of framing. 
\par We hope that some of the elements studied here will give us insights at the time of proposing a mathematical model about Mass Media and Public interaction. Future works may include a more systematic study and its extension to international Media, a deeper study of framing through topic detection and sentiment analysis, and a more quantitative analysis about causality.

@@

\subsubsection*{Current President}
\par \emph{Mauricio Macri} is the current Argentinian President, since December 2015. 
Most articles in political sections are logically devoted to him under different contexts.
However, it is important to point out that during the analyzed period, and specially after the general elections of October $22^{th}$, a controversial labour reform promoted by the government was been discussing.

\subsubsection*{\emph{Missing Person}}
\par \emph{Santiago Maldonado} vanished on August 1st after a minor clash between the Gendarmerie (Border Guards) and a group of Mapuches (Patagonian native population), which recognize as themselves the original population of an area in the Patagonia.
Since that event, the \emph{Mauricio Macri}'s administration was accused by several people as the responsible of a \textbf{forced disappearance}. 
\par A very massive campaign in social media took place on August $26^{th}$, under the motto ``Where is Santiago Maldonado?", followed by two massive protest marches to the \emph{Plaza de Mayo} that took place on September 1st and October 1st, which the first one had a great repercussion due to several incidents that took place during the march.
\par The body of \emph{Santiago Maldonado} was found on $17^{th}$ October in the \emph{Chubut} river, near the place where he was seen the last time, and the autopsy report told that \emph{Santiago Maldonado} had died from ``asphyxia after being submerged", with no injuries on his body. 
However the responsibility of the current administration is still being discussed.

@@

\par \emph{Julio de Vido} was the Planning minister during the administration of \emph{N\'estor Kirchner} and \emph{Cristina Fern\'andez de Kirchner} (2003-2015). In 2015, he was elected to integrate the Chamber of Deputies, which finally voted to strip \emph{De Vido} of his congressional immunity over corruption allegations and was immediatly jailed on October $27^{th}$.

\par \emph{Amado Boudou} was the Vice-President of the \emph{Cristina Kirchner}'s administration.
\emph{Boudou} was arrested on November 3th on charges including money-laundering and hiding undeclared assets.

@@

\par Naturally the topics found with LDA may not coincide with the NMF ones.
However, one expects that the corpus under study displays some degree of  robustness  when considering different topic model.
On the other hand, as was discussed in \cite{o2015analysis}, NMF can be a more suitable topic modeling method in certain domains, in the way that it produces more coherent topics, while LDA tends to return higher levels of generality and redundancy. Topic coherence is defined as the semantic interpretability of the terms used to describe a particular topic, although the coherence of a topic may depend on the end user's expectations.

@@

\begin{figure}[h!]
\includegraphics[width = \textwidth]{Fig1.pdf}
\caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic (then collapsed to seven) distribution and their corresponding wordclouds.} The Public Agenda is represented either by Google Trends (GT) and Twitter (Tw). Topics names are introduced together with the wordclouds containing the most important keywords involved in the definition of each topic. In green color we show the keywords used to define the topics in the Google Trends and Twitter queries (see table \ref{table:gt_queries}) and therefore in our construction of the Public Agenda.}
\label{fig:topics_wordclouds}
\end{figure}

\begin{figure}[h!]
\includegraphics[width = \textwidth]{Fig2.pdf}
\caption{\textbf{Bump graph of the time-dependent Media (MA) and Public Agendas extracted from Google Trends (GT) and Twitter (Tw)}. Widths and rankings of the curves encode topic's relative weight. Also, some important events related to the topics are pointed out:
\textbf{A}: First news about Santiago Maldonado's disappearance (Missing person);
\textbf{B}: Primary elections;
\textbf{C}: March one month after Santiago Maldonado's disappearance;
\textbf{D}: March two months after Santiago Maldonado's disappearance;
\textbf{E}: Appearance of Santiago Maldonado's body;
\textbf{F}: General elections;
\textbf{G}: Julio De Vido's detention;
\textbf{H}: Debates on labor reform;
\textbf{I}: Amado Boudou's detention (Former vice-president).
A more detailed explanation is given in section \ref{sec:Context}.}
\label{fig:all_agenda}
\end{figure}

\begin{figure}[h!]
\includegraphics[height=0.7\textheight]{Fig3.pdf}
\caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda show a less diverse behavior than the Media Agenda as can be seen in the top figure. The horizontal lines correspond to the lower inner fences of each signal in order to identify outliers. The related radar plots show  the agenda at the selected days where the time series exhibit dropouts (points a-d), indicating that the most important topic catches the most public's attention. \textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President. }
\label{fig:shannon_entropy_agendas}
\end{figure}
